Summary Tables

### 2023-11-29 summary_tables.Rmd
Uncomment code to display scenario definition

@@

# # rename scenarios
# rownames(scen_prop) <- unlist(lapply(rownames(scen_prop), FUN=get_qualified_scen_name))

# kable(scen_prop, headings = "Scenario Proportions")

>>>>

# Summary tables
List of tables for scenario, distance and duration

@@

# # rename scenarios
rownames(scen_prop) <- unlist(lapply(rownames(scen_prop), FUN=get_qualified_scen_name))

kable(scen_prop, headings = "Scenario Proportions")
